Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-06 WSSSPE3/report/WSSSPE3_review.tex
Neil's talk

\item \textbf{Neil Chue Hong: \textit{Building a Scientific Software Accreditation
Framework}}

>>>>

\item \textbf{Neil Chue Hong: \textit{Building a Scientific Software Accreditation
Framework}}
Neil Chue Hong presented a proposal to build a scientific software
accreditation framework. One of the aims of such a framework would be to
measure how ``good' a given software is, and to evaluate how this can be
effectively measured in the first place. This can be compared to the effort of
the standardized, easy to read and understand nutritional labelling of goods,
which only contain a small set of categories. However, such a framework for
software would have to be able to evaluate differently due to different
existing community norms. The challenges such a framework faces include that
many measurements are subjective, many metrics are too costly, and that
self-assessment needs to be encouraged. Possible categories would include
availability, usability, transferability, among others. Such a framework could
enable both improvement of specific software, as well as comparisons of similar
software. An accreditation by such a framework could then be part of software
management plans, ensuring that software is accessible and reusable throughout
the proposed project and beyond.
